Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 supplement.tex
induced list DSL

\subsection{List functions}

>>>>

\subsection{List functions}
\begin{verbatim}
#(\ (\ (index $0 (sort $1))))
#(\ (\ (slice $0 (+ $1 4))))
#(mapi (\ (\ (eq? $0 $2))))
#(\ (mapi (\ (\ (gt? $0 $2)))))
#(\ (any (\ (eq? $0 $1))))
#(\ (mapi (\ (\ (+ $0 $2)))))
#(\ (\ (mapi (\ (\ (index $2 $3))) $1)))
#(\ (mapi (\ (\ (mod $0 $2)))))
#(\ (mapi (\ (\ (* $0 $2)))))
#(\ (\ (singleton (index $0 $1))))
#(\ (\ (slice $0 (sum $1) $1)))
#(slice 0)
#(\ (\ (index (negate $0) (sort $1))))
#(\ (++ (singleton $0)))
#(\ (\ (++ $0 (singleton $1))))
#(\ (\ (++ $0 (singleton (index $1 $0)))))
#(\ (\ (++ (singleton (index $0 $1)) $1)))
#(\ (\ (\ (#(\ (mapi (\ (\ (mod $0 $2))))) $0 (#(\ (mapi (\ (\ (+ $0 $2))))) $1 $2)))))
#(\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))
#(#(\ (mapi (\ (\ (gt? $0 $2))))) 3 empty)
#(all (\ (is-square $0)))
#(\ (\ (#(\ (mapi (\ (\ (mod $0 $2))))) $0 (#(\ (mapi (\ (\ (+ $0 $2))))) 1 $1))))
#(\ (\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 $1))))
#(\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 2)))
#(filter (\ (#(\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 2))) (singleton $0))))
#(\ (\ (\ (++ (#(slice 0) $0 $1) (#(\ (\ (slice $0 (sum $1) $1))) $1 $2)))))
#(\ (filter (\ (#(\ (\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 $1)))) $1 (singleton $0)))))
#(filter (\ (not (#(\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 2))) (singleton $0)))))
#(\ (++ $0 (++ $0 $0)))
#(\ (++ $0 (#(\ (++ $0 (++ $0 $0))) $0)))
#(index 0)

\end{verbatim}
